---
title: "Analysis With Processed Data"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Loading, setting up

```{r}
library(tidyverse)
library(googlesheets4)
library(readxl)

# d <- read_csv("data/fall-2020-analyzing-data-in-science-survey.csv")

meta <- as_sheets_id("https://docs.google.com/spreadsheets/d/1gLyAAp6N_5g-Uo-eb61O-eW2apMzzqNdM8fLcBV7V3g/edit#gid=957320146")

meta

d <- read_sheet("https://docs.google.com/spreadsheets/d/1gLyAAp6N_5g-Uo-eb61O-eW2apMzzqNdM8fLcBV7V3g/edit#gid=957320146")

qual_q80 <- read_sheet("https://docs.google.com/spreadsheets/d/1gLyAAp6N_5g-Uo-eb61O-eW2apMzzqNdM8fLcBV7V3g/edit#gid=957320146", sheet = 8) %>% janitor::clean_names()

qual_q82 <- read_sheet("https://docs.google.com/spreadsheets/d/1gLyAAp6N_5g-Uo-eb61O-eW2apMzzqNdM8fLcBV7V3g/edit#gid=957320146", sheet = 15) %>% janitor::clean_names()
```

## agreement

```{r}
pa_irr_1 <- read_csv("pa-irr-data-sources-os.csv") %>% janitor::clean_names()
pa_irr_2 <- read_csv("pa-irr-data-sources-jr.csv") %>% janitor::clean_names()

check_agree <- function(pa_irr_1, pa_irr_2, n) {
  t <- data.frame(col1 = as.vector(pa_irr_1[, n]), col2 = as.vector(pa_irr_2[, n]))
  names(t) <- c("col1", "col2")
  t <- t %>% replace_na(list(col1 = 0, col2 = 0))
  list(irr::agree(t), irr::kappa2(t))
}

check_agree(pa_irr_1, pa_irr_2, 1)
check_agree(pa_irr_1, pa_irr_2, 2)
check_agree(pa_irr_1, pa_irr_2, 3)
check_agree(pa_irr_1, pa_irr_2, 4)
check_agree(pa_irr_1, pa_irr_2, 5)
check_agree(pa_irr_1, pa_irr_2, 6)
check_agree(pa_irr_1, pa_irr_2, 7)
check_agree(pa_irr_1, pa_irr_2, 8)
```

## Prepping and exploring grade bands

```{r}
d %>% 
  mutate(n_grades = str_count(grade_level_taught, ",")) %>% 
  count(n_grades)

d_grades <- d %>% 
  select(response_id, grade_level_taught) %>% 
  mutate(grade_level_taught = str_replace(grade_level_taught, ":", "")) %>% 
  separate(col = grade_level_taught, into = c(str_c("grade", letters[1:13])), sep = ",") %>% 
  gather(key, val, -response_id) %>% 
  arrange(response_id) %>% 
  mutate(val = as.integer(val)) %>% 
  mutate(elem = if_else(val <= 5, 1, 0)) %>% 
  mutate(second = if_else(val >= 6, 1, 0)) %>% 
  mutate(middle = if_else(val >= 6 & val <= 8, 1, 0)) %>% 
  mutate(high = if_else(val >= 9, 1, 0)) %>% 
  select(response_id, elem, second, middle, high) %>%
  group_by(response_id) %>% 
  summarize(elem = if_else(any(elem == 1), 1, 0),
            second = if_else(any(second == 1), 1, 0),
            middle = if_else(any(middle == 1), 1, 0),
            high = if_else(any(high == 1), 1, 0)) %>% 
  mutate_if(is.double, replace_na, 0)

d_grades %>% 
  count(elem, middle, high) %>% 
  knitr::kable()

# 194 only teach high
# 68 only teach middle
# 14 only teach elem

# 28 teach middle and high
# 8 teach elem and middle
# 10 teach all

# 8 teach none (remove?)
```

```{r}
d <- d %>% 
  left_join(d_grades)
```

## reasons for not using a tool

### overall

```{r}
d$q97 %>% is.na() %>% table()
table(d$q97 == "NA")

overall_q97 <- d %>% 
  select(response_id, elem, middle, high, q97) %>% 
  mutate(q97 = str_replace(q97, ", ", "; ")) %>%
  mutate(q97 = str_replace(q97, "etc\\.\\)", "")) %>%
  separate(col = q97, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  count(val) %>% 
  mutate(percent = n / 330) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3))

# p %>% 
#   ggplot(aes(x = reorder(val, percent), y = percent)) +
#   geom_col() +
#   coord_flip() +
#   xlab(NULL)
```

### cost - elem

```{r}
elem <- d %>% 
  select(response_id, elem, middle, high, q97) %>% 
  mutate(q97 = str_replace(q97, ", ", "; ")) %>%
  mutate(q97 = str_replace(q97, "etc\\.\\)", "")) %>%
  separate(col = q97, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(elem == 1) %>% # selecting elem
  count(val) %>% 
  mutate(percent = n / 32) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  select(val, elem = percent)
```

### cost - midd

```{r}
midd <- d %>% 
  select(response_id, elem, middle, high, q97) %>% 
  mutate(q97 = str_replace(q97, ", ", "; ")) %>%
  mutate(q97 = str_replace(q97, "etc\\.\\)", "")) %>%
  separate(col = q97, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(middle == 1) %>% # selecting elem
  count(val) %>% 
  mutate(percent = n /114) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  select(val, midd = percent)
```

### cost - high

```{r}
high <- d %>% 
  select(response_id, elem, middle, high, q97) %>% 
  mutate(q97 = str_replace(q97, ", ", "; ")) %>%
  mutate(q97 = str_replace(q97, "etc\\.\\)", "")) %>%
  separate(col = q97, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(high == 1) %>% # selecting elem
  count(val) %>% 
  mutate(percent = n / 232) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  select(val, high = percent)
```

### final table

```{r}
to_plot <- overall_q97 %>% 
  left_join(elem) %>% 
  left_join(midd) %>% 
  left_join(high) %>% 
  select(Barrier = val, n, overall = percent, elem, midd, high) %>% 
  mutate_if(is.integer, replace_na, 0)

to_plot %>% 
  filter(!str_detect(Barrier, "Other")) %>%
  knitr::kable()
```

## Tools used

### overall

```{r}
table(is.na(d$q78))
table(d$q78 == "NA")

overall_q78 <- d %>% 
  select(response_id, elem, middle, high, q78) %>% 
  mutate(q78 = str_replace(q78, ", ", "; ")) %>%
  mutate(q78 = str_replace(q78, "etc\\.\\)", "")) %>%
  separate(col = q78, into = c(str_c("grade", letters[1:12])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  count(val) %>% 
  mutate(percent = n / 330) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3))
```

### tools - elem

```{r}
elem <- d %>% 
  select(response_id, elem, middle, high, q78) %>% 
  mutate(q78 = str_replace(q78, ", ", "; ")) %>%
  mutate(q78 = str_replace(q78, "etc\\.\\)", "")) %>%
  separate(col = q78, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(elem == 1) %>% # selecting elem
  count(val) %>% 
  mutate(percent = n / 32) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  select(val, elem = percent)
```

### tools - midd

```{r}
midd <- d %>% 
  select(response_id, elem, middle, high, q78) %>% 
  mutate(q78 = str_replace(q78, ", ", "; ")) %>%
  mutate(q78 = str_replace(q78, "etc\\.\\)", "")) %>%
  separate(col = q78, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(middle == 1) %>% # selecting elem
  count(val) %>% 
  mutate(percent = n / 114) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  select(val, midd = percent)
```

### tools - high

```{r}
high <- d %>% 
  select(response_id, elem, middle, high, q78) %>% 
  mutate(q78 = str_replace(q78, ", ", "; ")) %>%
  mutate(q78 = str_replace(q78, "etc\\.\\)", "")) %>%
  separate(col = q78, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(high == 1) %>% # selecting elem
  count(val) %>% 
  mutate(percent = n / 232) %>%
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  select(val, high = percent)
```

### final table

```{r}
to_plot <- overall_q78 %>% 
  left_join(elem) %>% 
  left_join(midd) %>% 
  left_join(high) %>% 
  select(Technology = val, n, overall = percent, elem, midd, high) %>% 
  mutate_if(is.integer, replace_na, 0)

to_plot %>% 
  filter(!str_detect(Technology, "Other")) %>%
  knitr::kable()
```

## qual - q80

```{r}
d %>% filter(q80 != "NA")

# overall
qual_q80 %>% 
  select(3:9) %>% 
  summarize_all(sum, na.rm = T) %>% 
  gather(key, val) %>% 
  mutate(prop = val/328) %>% 
  arrange(desc(val)) %>% 
  knitr::kable()

qual_q80 %>% 
  left_join(d_grades) %>%
  select(3:9, elem, middle, high) %>%
  filter(elem == 1) %>% 
  summarize_at(vars(1:7), sum, na.rm = T) %>% 
  gather(key, val) %>% 
  mutate(prop = val/328) %>% 
  arrange(desc(val)) %>% 
  knitr::kable()

qual_q80 %>% 
  left_join(d_grades) %>%
  select(3:9, elem, middle, high) %>%
  filter(middle == 1) %>% 
  summarize_at(vars(1:7), sum, na.rm = T) %>% 
  gather(key, val) %>% 
  mutate(prop = val/328) %>% 
  arrange(desc(val)) %>% 
  knitr::kable()

qual_q80 %>% 
  left_join(d_grades) %>%
  select(3:9, elem, middle, high) %>%
  filter(high == 1) %>% 
  summarize_at(vars(1:7), sum, na.rm = T) %>% 
  gather(key, val) %>% 
  mutate(prop = val/328) %>% 
  arrange(desc(val)) %>% 
  knitr::kable()
```

## qual - q82

```{r}
d %>% filter(q82 != "NA")

qual_q82 %>% 
  select(3:10) %>% 
  summarize_all(sum, na.rm = T) %>% 
  gather(key, val) %>% 
  mutate(prop = val/330) %>% 
  arrange(desc(val)) %>% 
  knitr::kable()

qual_q82 %>% 
  left_join(d_grades) %>%
  select(3:10, elem, middle, high) %>%
  filter(elem == 1) %>% 
  summarize_at(vars(1:8), sum, na.rm = T) %>% 
  gather(key, val) %>% 
  mutate(prop = val/32) %>% 
  arrange(desc(val)) %>% 
  knitr::kable()

qual_q82 %>% 
  left_join(d_grades) %>%
  select(3:10, elem, middle, high) %>%
  filter(middle == 1) %>% 
  summarize_at(vars(1:8), sum, na.rm = T) %>% 
  gather(key, val) %>% 
  mutate(prop = val/114) %>% 
  arrange(desc(val)) %>% 
  knitr::kable()

qual_q82 %>% 
  left_join(d_grades) %>%
  select(3:10, elem, middle, high) %>%
  filter(high == 1) %>% 
  summarize_at(vars(1:8), sum, na.rm = T) %>% 
  gather(key, val) %>% 
  mutate(prop = val/234) %>% 
  arrange(desc(val)) %>% 
  knitr::kable()
```

### qual 82 - size

```{r}
qual_data_size <- qual_q82 %>% 
  left_join(d_grades) %>%
  select(3:11, elem, middle, high) %>% 
  rename(size = data_size_level_2_s_10_rows_2_columns_m_20_rows_3_4_columns_l_100s_of_rows_xl_thousands_of_rows)

qual_data_size %>% 
  filter(!is.na(size)) %>% 
  filter(size != "")

qual_data_size %>% 
  mutate(size = str_replace_all(size, "-", ",")) %>% 
  mutate(size = str_replace_all(size, "<", ",")) %>% 
  mutate(size = str_replace_all(size, " ", "")) %>% 
  mutate(size = ifelse(size == "small", "s", size)) %>% 
  mutate(size = tolower(size)) %>% 
  mutate(size = str_split(size, ",")) %>% 
  unnest(size) %>% 
  filter(!is.na(size)) %>% 
  filter(size != "") %>%
  count(size) %>% 
  mutate(prop = n / 96)
```

## Satisfaction

```{r}
# I am satisfied with the current data analysis tools that I use in my class. 
d %>% 
  mutate(q101_1_rc = case_when(
    q101_1 == "Strongly disagree" ~ 1,
    q101_1 == "Somewhat disagree" ~ 2,
    q101_1 == "Neither agree nor disagree" ~ 3,
    q101_1 == "Somewhat agree" ~ 4,
    q101_1 == "Strongly agree" ~ 5
  )) %>% 
  select(q101_1_rc) %>% 
  mutate(q101_1_rc = as.integer(q101_1_rc)) %>% 
  summarize(mean_var = mean(q101_1_rc, na.rm = TRUE),
            sd_var = sd(q101_1_rc, na.rm = T)) # 3.34 (1.04)

d %>% 
  mutate(q101_1_rc = case_when(
    q101_1 == "Strongly disagree" ~ 1,
    q101_1 == "Somewhat disagree" ~ 2,
    q101_1 == "Neither agree nor disagree" ~ 3,
    q101_1 == "Somewhat agree" ~ 4,
    q101_1 == "Strongly agree" ~ 5
  )) %>% 
  select(q101_1_rc, elem, middle, high) %>% 
  mutate(q101_1_rc = as.integer(q101_1_rc)) %>% 
  gather(key, val, -q101_1_rc) %>% 
  filter(val == 1) %>% 
  group_by(key) %>% 
  summarize(mean_var = mean(q101_1_rc, na.rm = TRUE),
            sd_var = sd(q101_1_rc, na.rm = T)) %>% 
  arrange(desc(mean_var))

# I use quantitative activities with my students regularly.
d %>% 
  mutate(q101_2_rc = case_when(
    q101_2 == "Strongly disagree" ~ 1,
    q101_2 == "Somewhat disagree" ~ 2,
    q101_2 == "Neither agree nor disagree" ~ 3,
    q101_2 == "Somewhat agree" ~ 4,
    q101_2 == "Strongly agree" ~ 5
  )) %>% 
  select(q101_2_rc) %>% 
  mutate(q101_2_rc = as.integer(q101_2_rc)) %>% 
  summarize(mean_var = mean(q101_2_rc, na.rm = TRUE),
            sd_var = sd(q101_2_rc, na.rm = T)) # 3.72 (1.03)

d %>% 
  mutate(q101_2_rc = case_when(
    q101_2 == "Strongly disagree" ~ 1,
    q101_2 == "Somewhat disagree" ~ 2,
    q101_2 == "Neither agree nor disagree" ~ 3,
    q101_2 == "Somewhat agree" ~ 4,
    q101_2 == "Strongly agree" ~ 5
  )) %>% 
  select(q101_2_rc, elem, middle, high) %>% 
  mutate(q101_2_rc = as.integer(q101_2_rc)) %>% 
  gather(key, val, -q101_2_rc) %>% 
  filter(val == 1) %>% 
  group_by(key) %>% 
  summarize(mean_var = mean(q101_2_rc, na.rm = TRUE),
            sd_var = sd(q101_2_rc, na.rm = T))%>% 
  arrange(desc(mean_var))

# I am interested in adding more quantitative activities into my class(es
d %>% 
  mutate(q101_3_rc = case_when(
    q101_3 == "Strongly disagree" ~ 1,
    q101_3 == "Somewhat disagree" ~ 2,
    q101_3 == "Neither agree nor disagree" ~ 3,
    q101_3 == "Somewhat agree" ~ 4,
    q101_3 == "Strongly agree" ~ 5
  )) %>% 
  select(q101_3_rc) %>% 
  mutate(q101_3_rc = as.integer(q101_3_rc)) %>% 
  summarize(mean_var = mean(q101_3_rc, na.rm = TRUE),
            sd_var = sd(q101_3_rc, na.rm = T)) # 4.41 (.75)

d %>% 
  mutate(q101_3_rc = case_when(
    q101_3 == "Strongly disagree" ~ 1,
    q101_3 == "Somewhat disagree" ~ 2,
    q101_3 == "Neither agree nor disagree" ~ 3,
    q101_3 == "Somewhat agree" ~ 4,
    q101_3 == "Strongly agree" ~ 5
  )) %>% 
  select(q101_3_rc, elem, middle, high) %>% 
  mutate(q101_3_rc = as.integer(q101_3_rc)) %>% 
  gather(key, val, -q101_3_rc) %>% 
  filter(val == 1) %>% 
  group_by(key) %>% 
  summarize(mean_var = mean(q101_3_rc, na.rm = TRUE),
            sd_var = sd(q101_3_rc, na.rm = T))%>% 
  arrange(desc(mean_var))
```

## PD

```{r}
d %>% 
  select(q99) %>% 
  janitor::tabyl(q99)

d %>% 
  filter(elem == 1) %>% 
  janitor::tabyl(q99)

d %>% 
  filter(middle == 1) %>% 
  janitor::tabyl(q99)

d %>% 
  filter(high == 1) %>% 
  janitor::tabyl(q99)
```

## first and second hand

```{r}
d %>% 
  select(response_id, q106) %>% 
  separate(col = q106, into = c(str_c("response_", letters[1:4])), sep = ",") %>% 
  gather(key, val, -response_id) %>% 
  arrange(response_id) %>% 
  count(val) %>% 
  mutate(prop = n / 330) %>% 
  filter(!is.na(n)) %>% 
  filter(val != "NA") %>% 
  arrange(desc(n))

d %>% 
  select(response_id, elem, middle, high, q106) %>% 
  separate(col = q106, into = c(str_c("response_", letters[1:4])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  arrange(response_id) %>% 
  filter(elem == 1) %>% 
  count(val) %>% 
  mutate(prop = n / 32) %>% # n elem 
  filter(!is.na(n)) %>% 
  filter(val != "NA") %>% 
  arrange(desc(n))

# 114, 232
d %>% 
  select(response_id, elem, middle, high, q106) %>% 
  separate(col = q106, into = c(str_c("response_", letters[1:4])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  arrange(response_id) %>% 
  filter(middle == 1) %>% 
  count(val) %>% 
  mutate(prop = n / 114) %>% # n elem 
  filter(!is.na(n)) %>% 
  filter(val != "NA") %>% 
  arrange(desc(n))

d %>% 
  select(response_id, elem, middle, high, q106) %>% 
  separate(col = q106, into = c(str_c("response_", letters[1:4])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  arrange(response_id) %>% 
  filter(high == 1) %>% 
  count(val) %>% 
  mutate(prop = n / 232) %>% # n elem 
  filter(!is.na(n)) %>% 
  filter(val != "NA") %>% 
  arrange(desc(n))
```

## demographics

```{r}
d %>% 
  count(gender) %>% 
  mutate(prop = n /330) # other is prefer not to say

d %>% 
  mutate(years_worked = unlist(years_worked)) %>% 
  mutate(years_worked = as.numeric(years_worked)) %>% 
  select(years_worked, elem, middle, high) %>% 
  filter(years_worked < 100) %>% # 2 outliers here
  summarize(mean_years_worked = mean(years_worked, na.rm = T),
            sd_years_worked = sd(years_worked, na.rm = T))

d %>% 
  count(underrepresented) %>% 
  mutate(prop = n / 330)

d %>% 
  count(with_which_groups) %>% 
  arrange(desc(n)) %>% 
  filter(with_which_groups != "NA") %>% 
  knitr::kable() # 9 African American/black (2.7%), 4 hispanic (1.2%), 2 asian (0.60%), 2 american indian, 1 muslim (0.30%)

```

## NSSME questions

### Organize and/or represent data using tables, charts, or graphs in order to facilitate analysis (4) - 1st - 34, 49, 58

```{r}
# Science Classes in Which Teachers Report Students Engaging in Various Aspects of Science Practices at Least Once a Week, by Grade Range

d %>% 
  filter(elem == 1) %>% 
  count(q98_3) %>% 
  filter(str_detect(q98_3, "Often") | str_detect(q98_3, "All")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32) # 34

d %>% 
  filter(middle == 1) %>% 
  count(q98_3) %>% 
  filter(str_detect(q98_3, "Often") | str_detect(q98_3, "All")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114) # 49

d %>% 
  filter(high == 1) %>% 
  count(q98_3) %>% 
  filter(str_detect(q98_3, "Often") | str_detect(q98_3, "All")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232) # 58

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_3) %>% 
  filter(str_detect(q98_3, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32) # 6

d %>% 
  filter(middle == 1) %>% 
  count(q98_3) %>% 
  filter(str_detect(q98_3, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114) # 1

d %>% 
  filter(high == 1) %>% 
  count(q98_3) %>% 
  filter(str_detect(q98_3, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232) # 1
```

### Analyze data using grade-appropriate methods in order to identify patterns, trends, or relationships (6) - 5th

```{r}

# at least once a week
d %>%
  filter(elem == 1) %>%
  count(q98_5) %>%
  filter(str_detect(q98_5, "Often") | str_detect(q98_5, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 32) # 27

d %>%
  filter(middle == 1) %>%
  count(q98_5) %>%
  filter(str_detect(q98_5, "Often") | str_detect(q98_5, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 114) # 43

d %>%
  filter(high == 1) %>%
  count(q98_5) %>%
  filter(str_detect(q98_5, "Often") | str_detect(q98_5, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 232) # 47

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_5) %>% 
  filter(str_detect(q98_5, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32) # 12

d %>% 
  filter(middle == 1) %>% 
  count(q98_5) %>% 
  filter(str_detect(q98_5, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114) # 3

d %>% 
  filter(high == 1) %>% 
  count(q98_5) %>% 
  filter(str_detect(q98_5, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232) # 3
```

### Determine which data would need to be collected in order to answer a scientific question (regardless of who generated the question) (1) - 5th

```{r}
# at least once a week
d %>%
  filter(elem == 1) %>%
  count(q98_1) %>%
  filter(str_detect(q98_1, "Often") | str_detect(q98_1, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 32) # 29

d %>%
  filter(middle == 1) %>%
  count(q98_1) %>%
  filter(str_detect(q98_1, "Often") | str_detect(q98_1, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 114) # 39

d %>%
  filter(high == 1) %>%
  count(q98_1) %>%
  filter(str_detect(q98_1, "Often") | str_detect(q98_1, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 232) # 39

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_1) %>% 
  filter(str_detect(q98_1, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32) # 8

d %>% 
  filter(middle == 1) %>% 
  count(q98_1) %>% 
  filter(str_detect(q98_1, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114) # 2

d %>% 
  filter(high == 1) %>% 
  count(q98_1) %>% 
  filter(str_detect(q98_1, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232) # 3
```

### Identify potential sources of variability (e.g., measurement error, natural variation) in the data (5) - NA

```{r}
# at least once a week
d %>%
  filter(elem == 1) %>%
  count(q98_4) %>%
  filter(str_detect(q98_4, "Often") | str_detect(q98_4, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 32)

d %>%
  filter(middle == 1) %>%
  count(q98_4) %>%
  filter(str_detect(q98_4, "Often") | str_detect(q98_4, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 114)

d %>%
  filter(high == 1) %>%
  count(q98_4) %>%
  filter(str_detect(q98_4, "Often") | str_detect(q98_4, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 232)

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_4) %>% 
  filter(str_detect(q98_4, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32)

d %>% 
  filter(middle == 1) %>% 
  count(q98_4) %>% 
  filter(str_detect(q98_4, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114)

d %>% 
  filter(high == 1) %>% 
  count(q98_4) %>% 
  filter(str_detect(q98_4, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232)
```

### Consider how missing data or measurement error can affect data interpretation (7)

```{r}
# at least once a week
d %>%
  filter(elem == 1) %>%
  count(q98_6) %>%
  filter(str_detect(q98_6, "Often") | str_detect(q98_6, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 32)

d %>%
  filter(middle == 1) %>%
  count(q98_6) %>%
  filter(str_detect(q98_6, "Often") | str_detect(q98_6, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 114)

d %>%
  filter(high == 1) %>%
  count(q98_6) %>%
  filter(str_detect(q98_6, "Often") | str_detect(q98_6, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 232)

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_6) %>% 
  filter(str_detect(q98_6, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32)

d %>% 
  filter(middle == 1) %>% 
  count(q98_6) %>% 
  filter(str_detect(q98_6, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114)

d %>% 
  filter(high == 1) %>% 
  count(q98_6) %>% 
  filter(str_detect(q98_6, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232)
```

### Select and use grade-appropriate mathematical and/or statistical techniques to analyze data (for example: determining the best measure of central tendency, examining variation in data, or developing a line of best fit) (9)

```{r}
# at least once a week
d %>%
  filter(elem == 1) %>%
  count(q98_7) %>%
  filter(str_detect(q98_7, "Often") | str_detect(q98_7, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 32)

d %>%
  filter(middle == 1) %>%
  count(q98_7) %>%
  filter(str_detect(q98_7, "Often") | str_detect(q98_7, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 114)

d %>%
  filter(high == 1) %>%
  count(q98_7) %>%
  filter(str_detect(q98_7, "Often") | str_detect(q98_7, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 232)

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_7) %>% 
  filter(str_detect(q98_7, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32)

d %>% 
  filter(middle == 1) %>% 
  count(q98_7) %>% 
  filter(str_detect(q98_7, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114)

d %>% 
  filter(high == 1) %>% 
  count(q98_7) %>% 
  filter(str_detect(q98_7, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232)
```

### Use mathematical and/or computational models to generate data to support a scientific claim (10)

```{r}
# at least once a week
d %>%
  filter(elem == 1) %>%
  count(q98_8) %>%
  filter(str_detect(q98_8, "Often") | str_detect(q98_8, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 32)

d %>%
  filter(middle == 1) %>%
  count(q98_8) %>%
  filter(str_detect(q98_8, "Often") | str_detect(q98_8, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 114)

d %>%
  filter(high == 1) %>%
  count(q98_8) %>%
  filter(str_detect(q98_8, "Often") | str_detect(q98_8, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 232)

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_8) %>% 
  filter(str_detect(q98_8, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32)

d %>% 
  filter(middle == 1) %>% 
  count(q98_8) %>% 
  filter(str_detect(q98_8, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114)

d %>% 
  filter(high == 1) %>% 
  count(q98_8) %>% 
  filter(str_detect(q98_8, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232)
```

### Use data and reasoning to defend, verbally or in writing, a claim or refute alternative scientific claims about a real-world phenomenon (regardless of who made the claims) (11)

```{r}
# at least once a week
d %>%
  filter(elem == 1) %>%
  count(q98_9) %>%
  filter(str_detect(q98_9, "Often") | str_detect(q98_9, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 32)

d %>%
  filter(middle == 1) %>%
  count(q98_9) %>%
  filter(str_detect(q98_9, "Often") | str_detect(q98_9, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 114)

d %>%
  filter(high == 1) %>%
  count(q98_9) %>%
  filter(str_detect(q98_9, "Often") | str_detect(q98_9, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 232)

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_9) %>% 
  filter(str_detect(q98_9, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32)

d %>% 
  filter(middle == 1) %>% 
  count(q98_9) %>% 
  filter(str_detect(q98_9, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114)

d %>% 
  filter(high == 1) %>% 
  count(q98_9) %>% 
  filter(str_detect(q98_9, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232)
```

### Determine which variables from a provided dataset are necessary to answer a scientific question (13)

```{r}
# at least once a week
d %>%
  filter(elem == 1) %>%
  count(q98_2) %>%
  filter(str_detect(q98_2, "Often") | str_detect(q98_2, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 32) # 29

d %>%
  filter(middle == 1) %>%
  count(q98_2) %>%
  filter(str_detect(q98_2, "Often") | str_detect(q98_2, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 114) # 39

d %>%
  filter(high == 1) %>%
  count(q98_2) %>%
  filter(str_detect(q98_2, "Often") | str_detect(q98_2, "All")) %>%
  summarize(n = sum(n)) %>%
  mutate(prop = n / 232) # 39

# never

d %>% 
  filter(elem == 1) %>% 
  count(q98_2) %>% 
  filter(str_detect(q98_2, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 32) # 8

d %>% 
  filter(middle == 1) %>% 
  count(q98_2) %>% 
  filter(str_detect(q98_2, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 114) # 2

d %>% 
  filter(high == 1) %>% 
  count(q98_2) %>% 
  filter(str_detect(q98_2, "Never")) %>% 
  summarize(n = sum(n)) %>% 
  mutate(prop = n / 232) # 3
```

## state

```{r}
d %>% count(state_work) %>%  # PR, outside US, 2 NA
  arrange(desc(n))
```
