---
title: "Analysis With Processed Data"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Loading, setting up

```{r}
library(tidyverse)

d <- read_csv("data/fall-2020-analyzing-data-in-science-survey.csv")
```

## Prepping and exploring grade bands

```{r}
d %>% 
  mutate(n_grades = str_count(grade_level_taught, ",")) %>% 
  count(n_grades)

d_grades <- d %>% 
  select(response_id, grade_level_taught) %>% 
  mutate(grade_level_taught = str_replace(grade_level_taught, ":", "")) %>% 
  separate(col = grade_level_taught, into = c(str_c("grade", letters[1:13])), sep = ",") %>% 
  gather(key, val, -response_id) %>% 
  arrange(response_id) %>% 
  mutate(val = as.integer(val)) %>% 
  mutate(elem = if_else(val <= 5, 1, 0)) %>% 
  mutate(second = if_else(val >= 6, 1, 0)) %>% 
  mutate(middle = if_else(val >= 6 & val <= 8, 1, 0)) %>% 
  mutate(high = if_else(val >= 9, 1, 0)) %>% 
  select(response_id, elem, second, middle, high) %>%
  group_by(response_id) %>% 
  summarize(elem = if_else(any(elem == 1), 1, 0),
            second = if_else(any(second == 1), 1, 0),
            middle = if_else(any(middle == 1), 1, 0),
            high = if_else(any(high == 1), 1, 0)) %>% 
  mutate_if(is.double, replace_na, 0)

d_grades %>% 
  count(elem, middle, high) %>% 
  knitr::kable()

# 194 only teach high
# 68 only teach middle
# 14 only teach elem

# 28 teach middle and high
# 8 teach elem and middle
# 10 teach all

# 8 teach none (remove?)
```

```{r}
d <- d %>% 
  left_join(d_grades)
```
## reasons for not using a tool
### overall
```{r}
overall_q97 <- d %>% 
  select(response_id, elem, middle, high, q97) %>% 
  mutate(q97 = str_replace(q97, ", ", "; ")) %>%
  mutate(q97 = str_replace(q97, "etc\\.\\)", "")) %>%
  separate(col = q97, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  janitor::tabyl(val) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3))

# p %>% 
#   ggplot(aes(x = reorder(val, percent), y = percent)) +
#   geom_col() +
#   coord_flip() +
#   xlab(NULL)
```
### cost - elem
```{r}
elem <- d %>% 
  select(response_id, elem, middle, high, q97) %>% 
  mutate(q97 = str_replace(q97, ", ", "; ")) %>%
  mutate(q97 = str_replace(q97, "etc\\.\\)", "")) %>%
  separate(col = q97, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(elem == 1) %>% # selecting elem
  janitor::tabyl(val) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  mutate(rank_order = dplyr::row_number()) %>% 
  select(val, elem = percent)
```
### cost - midd
```{r}
midd <- d %>% 
  select(response_id, elem, middle, high, q97) %>% 
  mutate(q97 = str_replace(q97, ", ", "; ")) %>%
  mutate(q97 = str_replace(q97, "etc\\.\\)", "")) %>%
  separate(col = q97, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(middle == 1) %>% # selecting elem
  janitor::tabyl(val) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  mutate(rank_order = dplyr::row_number()) %>% 
  select(val, midd = percent)
```
### cost - high
```{r}
high <- d %>% 
  select(response_id, elem, middle, high, q97) %>% 
  mutate(q97 = str_replace(q97, ", ", "; ")) %>%
  mutate(q97 = str_replace(q97, "etc\\.\\)", "")) %>%
  separate(col = q97, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(high == 1) %>% # selecting elem
  janitor::tabyl(val) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  mutate(rank_order = dplyr::row_number()) %>% 
  select(val, high = percent)
```
### final table
```{r}
to_plot <- overall_q97 %>% 
  left_join(elem) %>% 
  left_join(midd) %>% 
  left_join(high) %>% 
  select(Barrier = val, n, overall = percent, elem, midd, high) %>% 
  mutate_all(replace_na, 0)

to_plot %>% 
  filter(!str_detect(Barrier, "Other")) %>%
  knitr::kable()
```

## Tools used

### overall

```{r}
overall_q78 <- d %>% 
  select(response_id, elem, middle, high, q78) %>% 
  mutate(q78 = str_replace(q78, ", ", "; ")) %>%
  mutate(q78 = str_replace(q78, "etc\\.\\)", "")) %>%
  separate(col = q78, into = c(str_c("grade", letters[1:12])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  janitor::tabyl(val) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3))
```

### tools - elem
```{r}
elem <- d %>% 
  select(response_id, elem, middle, high, q78) %>% 
  mutate(q78 = str_replace(q78, ", ", "; ")) %>%
  mutate(q78 = str_replace(q78, "etc\\.\\)", "")) %>%
  separate(col = q78, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(elem == 1) %>% # selecting elem
  janitor::tabyl(val) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  mutate(rank_order = dplyr::row_number()) %>% 
  select(val, elem = percent)
```
### tools - midd
```{r}
midd <- d %>% 
  select(response_id, elem, middle, high, q78) %>% 
  mutate(q78 = str_replace(q78, ", ", "; ")) %>%
  mutate(q78 = str_replace(q78, "etc\\.\\)", "")) %>%
  separate(col = q78, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(middle == 1) %>% # selecting elem
  janitor::tabyl(val) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  mutate(rank_order = dplyr::row_number()) %>% 
  select(val, midd = percent)
```
### tools - high
```{r}
high <- d %>% 
  select(response_id, elem, middle, high, q78) %>% 
  mutate(q78 = str_replace(q78, ", ", "; ")) %>%
  mutate(q78 = str_replace(q78, "etc\\.\\)", "")) %>%
  separate(col = q78, into = c(str_c("grade", letters[1:9])), sep = ",") %>% 
  gather(key, val, -response_id, -elem, -middle, -high) %>% 
  filter(val!=" ") %>% 
  filter(!is.na(val)) %>% 
  filter(high == 1) %>% # selecting elem
  janitor::tabyl(val) %>% 
  arrange(desc(n)) %>% 
  mutate(percent = round(percent, 3)) %>% 
  mutate(rank_order = dplyr::row_number()) %>% 
  select(val, high = percent)
```

### final table

```{r}
to_plot <- overall_q78 %>% 
  left_join(elem) %>% 
  left_join(midd) %>% 
  left_join(high) %>% 
  select(Technology = val, n, overall = percent, elem, midd, high) %>% 
  mutate_all(replace_na, 0)

to_plot %>% 
  filter(!str_detect(Technology, "Other")) %>%
  knitr::kable()
```

## next steps

- create code to process qual data (should be relatively straightforward, but good to establish this)
- access code on computer that is presently being repaired so we can examine grade-level differences in these variables
- qual coding features desired in tech tools
